Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-22 paper/paper.Rmd
lots of figure tweaking + au redo

This paper tested the hypothesis that face typicality affects trustworthiness judgments such that the most typical face will be judged to be the most trustworthy. In Study 1, our target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive. While the original class projects selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis. We thus selected the interaction between face typicality and rating condition as our key test statistic and used the more standard by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model. Our replication study successfully showed this same interaction. We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face. Thus, despite replicating one key statistical test, our results are at odds with some of the original papers' claims.

>>>>

This paper tested the hypothesis that face typicality affects trustworthiness judgments such that the most typical face will be judged to be the most trustworthy. In Study 1, our target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive. While the original class projects selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis. We thus selected the interaction between face typicality and rating condition as our key test statistic and used the more standard by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model. Our replication study successfully showed this same interaction.^[We were unable to reproduce the numerical results from this model using the data from the original study, but we report the (larger) test statistics from our recomputed version.] We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face. Thus, despite replicating one key statistical test, our results are at odds with some of the original paper's claims.
